### 2015-04-08 related.tex
A correction to Indigo comparision

While serializing operations is sufficient to ensure that the application state
never violates invariants (e.g: \cf{balance $\ge$ 0}), there exist a range of
desirable application-level properties, which cannot be captured in Indigo's
specification language, or for which serialization is an overkill. For instance,
it is neither efficient nor straightforward in Indigo to declare and enforce a
condition to prevent the missing update anomaly
(Figure~\ref{fig:missingUpdateAnomaly}) in the bank account application. The
only way is to encode specifications of all bank account operations such that
every pair of operations are identified as $I$-offending, for some invariant
($I$), resulting in them being serialized. In contrast, \name's contract
language allows for precise encoding of the desired property, and the contract
classification scheme ensures that the it can be enforced without the need to
serialize operations. Furthermore, Indigo also does not distinguish between
various transaction isolation guarantees, which \name does.

>>>>

While serializing operations is sufficient to ensure that the application state
never violates invariants (e.g: \cf{balance $\ge$ 0}), there exist a range of
desirable application-level properties, which cannot be captured in Indigo's
specification language, or for which serialization is an overkill. For instance,
it is neither efficient nor straightforward in Indigo to declare and enforce a
condition to prevent the missing update anomaly
(Figure~\ref{fig:missingUpdateAnomaly}) in the bank account application. The
only way is to encode specifications of bank account operations such that pairs
of \cf{getBalance} and \cf{withdraw}, and \cf{getBalance} and \cf{deposit}
operations are identified as $I$-offending, resulting in them being serialized.
In contrast, \name's contract language allows for precise encoding of the
desired property, and the contract classification scheme ensures that the it can
be enforced without the need to serialize operations.  Furthermore, Indigo also
does not distinguish between various transaction isolation guarantees, which
\name does.
